\chapter{Preliminaries: Set theory and categories}
\section{Naive set theory}
\problem{
    Locate a discussion of Russell's paradox, and understand it.
}{
    Recall that, in naive set theory, any collection of objects satisfying some properties can be called a set. Russel's paradox can be illustrated as follows:

    Let $R$ be the set of all sets that do not contain themselves. Then, if $R \notin R$, then by definition it must be the case that $R \in R$. Similarly, if $R \in R$ then it must be the case that $R \notin R$.

    This is the reason why we need the axiomatic set theory instead of the naive set theory.
}

\problem{
    $\vartriangleright$ Prove that if $\sim$ is an equivalence relation on a set $S$, then the corresponding family $\mathscr{P}_\sim$ defined in \S 1.5 is indeed a partition of $S$; that is, its elements are nonempty, disjoint, and their union is $S$. $\left[ \text{\S1.5} \right]$
}{
    Let $S$ be a set with an equivalence relation $\sim$. Consider the family of equivalence classes with respect to $\sim$ over $S$:
    $$\mathscr{P}_\sim = \{ \left[ a \right]_\sim \mid a \in S \}$$

    Let $\left[ a \right]_\sim \in \mathscr{P}_\sim$. Then by reflexivity of $\sim$, we have $a \sim a$ and thus $\left[ a \right]_\sim$ is nonempty. 

    Now, take any two elements $\left[ a \right]_\sim$ and $\left[ b \right]_\sim$ of $\mathscr{P}_\sim$. If $\left[ a \right]_\sim \cap \left[ b \right]_\sim$ is nonempty, then we can take an element $c \in \left[ a \right]_\sim \cap \left[ b \right]_\sim$. By definition, we get $c \sim a$ and $c \sim b$. By symmetricity of $\sim$, we get $a \sim c$ and so $a \sim b$ by transitivity of $\sim$. This means that $a \in \left[ b \right]_\sim$, and by transitivity of $\sim$, we can conclude that $\left[ a \right]_\sim \subseteq \left[ b \right]_\sim$.

    In the same way, we also can conclude that $\left[ b \right]_\sim \subseteq \left[ a \right]_\sim$ when $\left[ a \right]_\sim \cap \left[ b \right]_\sim$ is nonempty, and hence $\left[ a \right]_\sim = \left[ b \right]_\sim$ if $\left[ a \right]_\sim \cap \left[ b \right]_\sim$ is nonempty. In the other words, the elements of $\mathscr{P}_\sim$ are disjoint.
    
    Finally, for any $a \in S$, $a \in \left[ a \right]_\sim$, and thus $S \subseteq \bigcup \mathscr{P}_\sim$, obviously. Also, since $\sim$ is a relation on the set $S$, $\bigcup \mathscr{P}_\sim \subseteq S$, indeed.

    Therefore, $\mathscr{P}_\sim$ is a partition of $S$.
}

\problem{
    $\vartriangleright$ Given a partition $\mathscr{P}$ on a set $S$, show how to define an equivalence relation $\sim$ on $S$ such that $\mathscr{P}$ is the corresponding partition. $\left[ \text{\S1.5} \right]$
}{
    Let $S$ be a set with a partition $\mathscr{P}$. Consider a relation $\sim$ on $S$ as:
    $$a \sim b \iff \exists P \in \mathscr{P} \st a,b \in P.$$

    Then, it is quite obvious that $\sim$ is an equivalence relation.
}

\problem{
    How many different equivalence relations may be defined on the set $\{ 1,2,3 \}$?
}{
    Since there is a correspondence between equivalence relations and partitions, the number of equivalence relations is the same with the number of partitions. Since there are 5 different partitions of the set $\{ 1,2,3 \}$, there are 5 different equivalence relations can be defined on the set $\{ 1,2,3 \}$.
}

\problem{
    Give an example of a relation that is reflexive and symmetric but not transitive. What happens if you attempt to use this relation to define a partition on the set?
}{
    For $a,b \in \RR$, define $a \mathrel{\mathcal{R}} b$ to be true if and only if $\abs{a-b} \leq 1$. Then, it is obvious that $\mathrel{\mathcal{R}}$ is reflexive and symmetric. However, since $0 \not\mathrel{\mathcal{R}} 2$ even though $0 \mathrel{\mathcal{R}} 1$ and $1 \mathrel{\mathcal{R}} 2$, $\mathrel{\mathcal{R}}$ is not transitive. The corresponding family $\mathscr{P}_{\mathrel{\mathcal{R}}}$, defined as in \S 1.5, is not a partition of $\RR$, indeed  because the elements of $\mathscr{P}_{\mathrel{\mathcal{R}}}$ are not disjoint.
}

\problem{
    $\vartriangleright$ Define a relation $\sim$ on the set $\RR$ of real numbers by setting $a \sim b \iff b-a \in \ZZ$.  Prove that this is an equivalence relation, and find a `compelling' description for $\RR / \sim$. Do the same for the relation $\approx$ on the plane $\RR \times \RR$ defined by declaring  $\left( a_1,a_2 \right) \approx \left( b_1,b_2 \right) \iff b_1 - a_1 \in \ZZ$ and $b_2 - a_2 \in \ZZ$.  $\left[ \text{\S{}II.8.1, II.8.10} \right]$
}{
    Since $0 \in \ZZ$, $-n \in \ZZ$ for any $n \in \ZZ$, and $n+m \in \ZZ$ for any $n,m \in \ZZ$, the given relation $\sim$ on $\RR$ is an equivalence relation. Moreover, $\RR / \sim$ can be considered as $\lcint{0}{1}$ with operation on modulo 1. (It can be considered as $S^1$.)

    Now define a relation $\approx$ on $\RR^2$ by setting $\left( a_1,a_2 \right) \approx \left( b_1,b_2 \right) \iff a_1 - a_2 \in \ZZ$ and $b_1 - b_2 \in \ZZ$. Then by the similar way with the above, the relation $\approx$ on $\RR^2$ is an equivalence relation. Additionally, $\RR^2 / \approx$ is isomorphic to $\lcint{0}{1} \times \lcint{0}{1}$ with operation on modulo 1. (It can be considered as $T^2$.)
}

\newpage
\section{Functions between Sets}

\problem{
    $\vartriangleright$ How many different bijections are there between a set $S$ with $n$ elements and itself?
}{
    The answer is $n!$, obviously.
}

\problem{
    $\vartriangleright$ Prove statement (2) in Proposition 2.1. You may assume that given a family of disjoint nonempty subsets of a set, there is a way to choose one element in each member of the family. $\left[ \text{\S2.5, V.3.3} \right]$
}{
    \begin{itemize}[leftmargin=12mm]
        \item[]
        \item[($\implies$)] Let's say that $f : A \to B$ has a right-inverse $g : B \to A$. Then since $f \circ g = \id_B$, $(f \circ g)(B) = B$, clearly.
        
        By the fact that $(f \circ g)(B) = f(g(B)) \subseteq f(A) \subseteq B$, it is immediately shown that $f(A) = B$, i.e., $f$ is surjective.
        
        \item[($\impliedby$)] Let's say that $f : A \to B$ is surjective. Then $f^{-1}(b) = \{ a \in A \mid f(a) = b \}$ is nonempty for any $b$ and also $\{ f^{-1}(b) \mid b \in B \}$ is a partition of $A$, clearly.

        Thus, by the axiom of choice---the given statement is the stronger version of the axiom of choice, we can take a function $g : B \to A$ such that $g(b) \in f^{-1}(b)$ for any $b \in B$.

        Then $(f \circ g)(b) = b$ for any $b \in B$ and $f$ therefore has a right-inverse $g : B \to A$.
    \end{itemize}
}

\problem{
    Prove that the inverse of a bijection is a bijection and that the composition of two bijection is a bijection.
}{
    By Proposition 2.1, it is clear that the inverse of a bijection is also a bijection and that the composition of two bijections is also a bijection.
}

\problem{
    $\vartriangleright$ Prove that `isomorphism' is an equivalence relation (on any set of sets). \(\left[ \text{\S4.1} \right]\)
}{
    Let $U$ be a set of sets and define a relation $\sim$ on $U$ by setting $S \sim T \iff S$ is isomorphic to $T$.
    
    Then it is clear that $S \sim S$ for any $S \in U$ since $\id_S$ is a bijection.

    Moreover, by the result of the Exercise 2.3, the relation $\sim$ on $U$ is symmetric and transitive.
    
    Therefore, the relation $\sim$ on $U$ is an equivalence relation.
}

\problem{
    $\vartriangleright$ Formulate a notion of \emph{epimorphism}, in the style of the notion of \emph{monomorphism} seen in \S2.6, and prove a result analogous to Proposition 2.3, for epimorphism and surjections. \(\left[ \S2.6, \S4.2 \right]\)
}{
    A function $f : A \to B$ is an epimorphism if the following holds:
    \begin{center}
        for all sets $Z$ and all functions $\alpha', \alpha'' : B \to Z$, $\alpha' \circ f = \alpha'' \circ f \implies \alpha' = \alpha''$.
    \end{center}

    Now claim that a function $f : A \to B$ is an epimorphism if and only if it is a surjection. The below is the proof of that:

    \begin{itemize}[leftmargin=12mm]
        \item[($\implies$)] Let's say that $f : A \to B$ is an epimorphism and suppose that $f$ is not surjective. Then $B \setminus f(A)$ is nonempty and so there exists $b \in B \setminus f(A)$. Now say that $\alpha' = \id_B$ and $\alpha'' : B \to B$ is defined by $x \mapsto \begin{cases}x & \mbox{if } x \neq b \\ b' & \mbox{if } x=b\end{cases}$ where $b'$ is an element of $f(A)$.

        Then it is obvious that $\alpha' \circ f = \alpha'' \circ f$ and this contradicts the fact that $f$ is an epimorphism.

        Therefore, $f$ has to be surjective.
        
        \item[($\impliedby$)] Let's say that $f : A \to B$ is a surjection and $\alpha' \circ f = \alpha'' \circ f$ for some $\alpha', \alpha'' : B \to Z$ for a fixed set $Z$.
        
        Then since $f(A) = B$, $\alpha' \circ f = \alpha'' \circ f$ implies that $\alpha'(b) = \alpha''(b)$ for any $b \in B$, and this clearly implies that $\alpha' = \alpha''$.

        Therefore, $f$ is an epimorphism.
    \end{itemize}
}

\problem{
    With notation as in Example 2.4, explain how any function $f : A \to B$ determines a section of $\pi_A$.
}{
    Define $\gamma_f : A \to A \times B$ as $a \mapsto \left( a,f(a) \right)$. Then $\left( \pi_A \circ \gamma_f \right)(a) = \pi_A \left( a,f(a) \right) = a$ and thus makes $\gamma_f$ be a right-inverse of $\pi_A$, i.e., $\gamma_f$ is a section of $\pi_A$.
}

\problem{
    Let $f : A \to B$ be any function. Prove that the graph $\Gamma_f$ of $f$ is isomorphic to $A$.
}{
    Let $\varphi : A \to \Gamma_f$ be a function defined as $\varphi : a \mapsto \left( a,f(a) \right)$.

    Then it is obvious that $\varphi$ is a bijection by the definition of a graph of a function. Therefore, $A$ and $\Gamma_f$ are isomorphic to each other.
}

\problem{
    Describe as explicitly as you can all terms in the canonical decomposition (cf. \S2.8) of the function $\RR \to \CC$ defined by $r \mapsto e^{2\pi ir}$. (This exercise matches one assigned previously. Which one?)
}{
    Let $f : \RR \to \CC$ be defined by $r \mapsto e^{2\pi ir}$.

    Now let's say that $\pi : \RR \twoheadrightarrow \lcint{0}{1}$, $\tilde{f} : \lcint{0}{1} \twoheadhookrightarrow \{ z \in \CC \mid \abs{z} = 1 \}$, and $\iota : \{ z \in \CC \mid \abs{z} = 1 \} \to \CC$ are defined as:
    $$\begin{array}{l}
        \pi : r \mapsto r \bmod 1 \\
        \tilde{f} : r \mapsto e^{2\pi ir} \\
        \iota : z \mapsto z.
    \end{array}$$

    Then, $f = \iota \circ \tilde{f} \circ \pi$ is the canonical decomposition of $f$. Also, this exercise matches Exercise 1.6.
}

\problem{
    $\vartriangleright$ Show that if $A' \cong A''$ and $B' \cong B''$, and further $A' \cap B' = \emptyset$ and $A'' \cap B'' = \emptyset$, then $A' \cup B' \cong A'' \cup B''$. Conclude that the operation $A \sqcup B$ (as described in \S1.4) is well-defined \emph{up to isomorphism} (cf. \S2.9). $\left[ \text{\S2.9, 5.7} \right]$
}{
    Since $A' \cap B' = \emptyset$, if $x \in A' \cup B'$, only one of the following holds:
    \begin{enumerate}[label=\alph*)]
        \item $x \in A'$
        \item $x \in B'$
    \end{enumerate}
    Furthermore, $A''$ and $B''$ also satisfy the same property.

    Now let $\alpha : A' \to A''$ and $\beta : B' \to B''$ be bijections. Then we can define a function $\varphi : A' \cup B' \to A'' \cup B''$ as $x \mapsto \begin{cases} \alpha(x) & \mbox{if } x \in A' \\ \beta(x) & \mbox{if } x \in B'. \end{cases}$

    By the facts proved above, $\varphi$ is obviously a bijection. Therefore, $A' \cong A''$, $B' \cong B''$, $A' \cap B' = \emptyset$, and $A'' \cap B'' = \emptyset$ imply that $A' \cup B' \cong A'' \cup B''$ and, hence, the operation $A \sqcup B$ is well-defined up to isomorphism.
}

\problem{
    $\vartriangleright$ Show that if $A$ and $B$ are finite sets, $\abs{B^A} = \abs{B}^{\abs{A}}$. \(\left[ \text{\S2.1, 2.11, \S II.4.1}\right]\)
}{
    Since $A^B$ is the set of the functions to $A$ from $B$, $\abs{B^A}$ is the number of functions from $A$ to $B$. For each element of $A$, there exist $\abs{B}$ possible function values and thus $\abs{B^A} = \abs{B}^{\abs{A}}$.
}

\problem{
    $\vartriangleright$ In view of Exercise 2.10, it is not unreasonable to use $2^A$ to denote the set of functions from an arbitrary set $A$ to set with 2 elements (say $\{ 1,2 \}$). Prove that there is a bijection between $2^A$ and the \emph{power set} of $A$ (cf. \S1.2). \(\left[ \S1.2, III.2.3 \right]\)
}{
    Define $f : 2^A \to \mathscr{P}(A)$ as $\varphi \mapsto \{ a \in A \mid \varphi(a) = 1 \}$. Then it is quite obvious that $f$ is a bijection. Therefore, $2^A \cong \mathscr{P}(A)$.
}

\newpage
\section{Categories}
\problem{
    $\vartriangleright$ Let $\cat{C}$ be a category. Consider a structure $\op{\cat{C}}$ with
    \begin{itemize}[label=\bullet]
        \item $\Obj{\op{\cat{C}}} := \Obj{\cat{C}}$
        \item for $A$, $B$ objects of $\op{\cat{C}}$ (hence objects of $\cat{C}$), $\Hom{\op{\cat{C}}}{A}{B} := \Hom{\cat{C}}{B}{A}$.
    \end{itemize}
    Show how to make this into a category (that is, define composition of morphisms in $\op{\cat{C}}$ and verify the properties listed in \S3.1).
}{

}

\problem{
    If $A$ is a finite set, how large is $\End{\Set}{A}$?
}{

}

\problem{
    $\vartriangleright$ Formulate precisely what it means to say that $\one_a$ is an identity with respect to composition in Example 3.3, and prove this assertion. \(\left[ \text{\S3.2} \right]\)
}{

}

\problem{
    Can we define a category in the style of Example 3.3 using the relation $<$ on the set $\ZZ$?
}{

}

\problem{
    $\vartriangleright$ Explain in what sense Example 3.4 is an instance of the categories considered in Example 3.3. \(\left[ \text{\S3.2} \right]\)
}{

}

\problem{
    $\vartriangleright$ (Assuming some familiarity with linear algebra.) Define a category $\cat{V}$ by taking $\Obj{\cat{V}} = \NN$ and letting $\Hom{\cat{V}}{n}{m} = \text{the set of } m \times n$ matrices with real entries, for all $n,m \in \NN$. (We will leave the reader the task of making sense of a matrix with 0 rows or columns.) Use product of matrices to define composition. Does this category `feel' familiar? \(\left[ \text{\S VI.2.1, \S VIII.1.3} \right]\)
}{

}

\problem{
    $\vartriangleright$ Define carefully objects and morphisms in Example 3.7, and draw the diagram corresponding to composition. \(\left[ \text{\S3.2} \right]\)
}{

}

\problem{
    $\vartriangleright$ A \emph{subcategory} $\cat{C'}$ of a category $\cat{C}$ consists of a collection of objects of $\cat{C}$, with morphisms $\Hom{\cat{C'}}{A}{B} \subseteq \Hom{\cat{C}}{A}{B}$ for all objects $A$, $B$ in $\Obj{\cat{C'}}$, such that identities and compositions in $\cat{C}$ make $\cat{C'}$ into a category. A subcategory $\cat{C'}$ is \emph{full} if $\Hom{\cat{C'}}{A}{B} = \Hom{\cat{C}}{A}{B}$ for all $A,B$ in $\Obj{\cat{C'}}$. Construct a category of \emph{infinite sets} and explain how it may be viewed as a full subcategory of $\Set$. \(\left[ \text{4.4, \S VI.1.1, \S VIII.1.3 }\right]\)
}{

}

\problem{
    $\vartriangleright$ An alternative to the notion of \emph{multiset} introduced in \S2.2 is obtained by considering sets endowed with equivalence relatoins; equivalent elements are taken to be multiple instances of elements `of the same kind'. Define a notion of morphism between such enhanced sets, obtaining a category $\MSet$ containing (a `copy' of) $\Set$ as a full subcategory. (There may be more than one reasonable way to do this! This is intentionally an open-ended exercise.) Which objects in $\MSet$ determine ordinary multisets as defined in \S2.2 and how? Spell out what a morphism of multisets would be from this point of view. (There are several natural notions of morphisms of multisets. Try to define morphisms in $\MSet$ so that the notion you obtain for ordinary multisets captures your intuitive understanding of these objects.) \(\left[ \text{\S2.2, \S3.2, 4.5} \right]\)
}{

}

\problem{
    Since the objects of a category $\cat{C}$ are not (necessarily) sets, it is not clear how to make sense of notion of `subobject' in general. In some situations it \emph{does} make sense to talk about subobjects, and the subobjects of any given object $A$ in $\cat{C}$ are in one-to-one correspondence with the morphisms $A \to \Omega$ for a fixed, special object $\Omega$ of $\cat{C}$, called a \emph{subobject classifier}. Show that $\Set$ has a subobject classifier.
}{

}

\problem{
    $\vartriangleright$ Draw the relevant diagrams and define composition and identities for the category $\cat{C}^{A,B}$ mentioned in Example 3.9. Do the same for the category $\cat{C}^{\alpha, \beta}$ mentioned in Example 3.10. \(\left[ \text{\S5.5, 5.12} \right]\)
}{
    
}